---
title: "subject6"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

```{r}
data = read.csv(file = 'Subject6_smoking.csv')
head(data,5)
```
# 1
## Two way table betwen if they are alive or dead and if yes or no they smoke
```{r}
datatable = table(data$Smoker, data$Status)
addmargins(datatable)
```

```{r}
barplot(datatable, legend=TRUE, beside=TRUE, main='Alive-Dead count by Smoking-NonSmoking')
```
```{r}
#rate of death in the smoking and non smoking categories
rate_vector = (addmargins(datatable)[, 'Dead'] / addmargins(datatable)[, 'Sum'])[c('No', 'Yes')]
barplot(rate_vector, main="Rate of death if yes or no women smoke")
```

## Explanation
We can observe that the rate of mortality is higher in the women that didn't smoke and that is suprising because we would expect the contrary.

# 2

```{r}
data_18_34 = data[data$Age > 18 & data$Age < 34, ]
datatable_18_34 = addmargins(table(data_18_34$Smoker, data_18_34$Status))
datatable_18_34
```
```{r}
rate_vector_18_34 = (datatable_18_34[, 'Dead'] / datatable_18_34[, 'Sum'])[c('No', 'Yes')]
barplot(rate_vector_18_34, main="Rate of death for women between 18 and 34 if yes or no they smoke")
```
```{r}
data_34_54 = data[data$Age >= 34 & data$Age < 54, ]
datatable_34_54 = addmargins(table(data_34_54$Smoker, data_34_54$Status))
datatable_34_54
```

```{r}
rate_vector_34_54 = (datatable_34_54[, 'Dead'] / datatable_34_54[, 'Sum'])[c('No', 'Yes')]
barplot(rate_vector_34_54, main="Rate of death for women between 34 and 54 if yes or no they smoke")
```
Women wo smoke die more in this category.
```{r}
data_54_65 = data[data$Age >= 54 & data$Age < 65, ]
datatable_54_65 = addmargins(table(data_54_65$Smoker, data_54_65$Status))
datatable_54_65
```
```{r}
rate_vector_54_65 = (datatable_54_65[, 'Dead'] / datatable_54_65[, 'Sum'])[c('No', 'Yes')]
barplot(rate_vector_54_65, main="Rate of death for women between 54 and 65 if yes or no they smoke")
```
Women wo smoke die more in this category.
```{r}
data_65 = data[data$Age >= 65, ]
datatable_65 = addmargins(table(data_65$Smoker, data_65$Status))
datatable_65
```

## Explanations
We can observe that for womens older than 65, there is much more deaths in the category that don't smoke. This make the data unbalance. This high number of death brings the total rate as observe previously to a high number.
```{r}
rate_vector_65 = (datatable_65[, 'Dead'] / datatable_65[, 'Sum'])[c('No', 'Yes')]
barplot(rate_vector_65, main="Rate of death for women of more than 65 if yes or no they smoke")
```
The relative rate in this category is similar thought.

# 3
```{r}
#change Alive and Dead in 0 and 1 in the Status column
data1 <- data %>%
      mutate(Status = ifelse(Status == "Alive",0,1))

data_no = data1[data1$Smoker == 'No',]
#plot logistic regression curve
ggplot(data_no, aes(x=Age, y=Status)) + 
  geom_point(alpha=.5) +
  stat_smooth(method="glm", method.args = list(family=binomial))+
  labs(
    y = "Probability of Dying"
    )
```
```{r}
data_yes = data1[data1$Smoker == 'Yes',]
#plot logistic regression curve
ggplot(data_yes, aes(x=Age, y=Status)) + 
  geom_point(alpha=.5) +
  stat_smooth(method="glm", method.args = list(family=binomial)) +
  labs(
    y = "Probability of Dying"
    )
```

## Explanation

We can observe that the probability of death increase more quickly for the womens that smoke
